Pancreatic endocrinogenesis

### 2024-08-07 nbs/tutorials/pancreas/results/pancreas.qmd
fix(nbs): add parameter posterior estimates to pancreas results
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

@@

>>>>

It is somewhat difficult to compare the parameter posteriors on a common scale
but we plot their posterior distributions below.

```{python}
# | label: model1-generate-parameter-posterior-plot
# | output: false
from pyrovelocity.plots import plot_parameter_posterior_distributions

posterior_samples.pop("t0", None)

plot_parameter_posterior_distributions(
    posterior_samples=posterior_samples,
    adata=adata,
    geneset=putative_marker_genes,
    parameter_uncertainty_plot="model1_parameter_uncertainty_plot.pdf",
)
```

```{python}
# | label: model1-show-parameter-posterior-plot
# | code-fold: true
# | output: true
display(Image(filename=f"model1_parameter_uncertainty_plot.pdf.png"))
```

@@

Finally, we plot the parameter posteriors for the second model.

```{python}
# | label: model2-generate-parameter-posterior-plot
# | output: false
from pyrovelocity.plots import plot_parameter_posterior_distributions

plot_parameter_posterior_distributions(
    posterior_samples=posterior_samples,
    adata=adata,
    geneset=putative_marker_genes,
    parameter_uncertainty_plot="model2_parameter_uncertainty_plot.pdf",
)
```

```{python}
# | label: model2-show-parameter-posterior-plot
# | code-fold: true
# | output: true
display(Image(filename=f"model2_parameter_uncertainty_plot.pdf.png"))
```
